---
title: "RSS Feed Reader"
format:
  html:
    page-layout: full
execute:
  echo: false
  message: false
  warning: false
---

<style>
.page-container {
  display: grid;
  grid-template-columns: 250px 1fr;
  gap: 2rem;
  max-width: 1400px;
  margin: 0 auto;
  padding: 2rem;
}

.feed-sidebar {
  position: sticky;
  top: 2rem;
  height: fit-content;
}

.feed-sidebar h3 {
  font-size: 1rem;
  margin-bottom: 1rem;
  color: var(--color-muted);
  text-transform: uppercase;
  letter-spacing: 0.5px;
}

.feed-list {
  list-style: none;
  padding: 0;
}

.feed-item {
  padding: 0.5rem 0.75rem;
  margin-bottom: 0.25rem;
  border-radius: 4px;
  cursor: pointer;
  transition: all 0.2s;
  font-size: 0.9rem;
  border: 1px solid transparent;
}

.feed-item:hover {
  background-color: var(--color-light-bg);
  border-color: var(--color-border);
}

.feed-item.active {
  background-color: rgba(0, 85, 204, 0.1);
  border-color: var(--color-accent);
  color: var(--color-accent);
  font-weight: 600;
}

.feed-count {
  float: right;
  font-size: 0.8rem;
  color: var(--color-muted);
}

.load-more-btn {
  display: block;
  width: 100%;
  max-width: 300px;
  margin: 2rem auto;
  padding: 1rem 2rem;
  background-color: var(--color-accent);
  color: white;
  border: none;
  border-radius: 4px;
  font-size: 1rem;
  font-weight: 500;
  cursor: pointer;
  transition: background-color 0.2s;
}

.load-more-btn:hover {
  background-color: var(--color-accent-hover);
}

.load-more-btn:disabled {
  opacity: 0.5;
  cursor: not-allowed;
}

.main-content {
  min-width: 0;
}

@media (max-width: 768px) {
  .page-container {
    grid-template-columns: 1fr;
  }

  .feed-sidebar {
    position: static;
    margin-bottom: 2rem;
  }
}
</style>

```{r setup}
# Load required libraries
suppressPackageStartupMessages({
  library(tidyRSS)
  library(dplyr)
  library(yaml)
  library(lubridate)
  library(stringr)
})

# Source helper scripts
source("scripts/fetch-feeds.R")
source("scripts/process-feeds.R")
source("scripts/utils.R")
```

```{r fetch-data}
# Fetch and process all RSS feeds
raw_articles <- fetch_all_feeds()
articles <- process_articles(raw_articles)

# Get statistics
total_articles <- nrow(articles)
feed_counts <- articles %>%
  group_by(source) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count))
```

::: {.hero}
# 📰 Latest News

Aggregating **`r total_articles`** articles from **`r nrow(feed_counts)`** sources

*Updated: `r format(Sys.time(), "%B %d, %Y at %I:%M %p")`*
:::

```{r render-page}
#| results: asis

cat('<div class="page-container">')

# === LEFT SIDEBAR: Feed Filter ===
cat('<aside class="feed-sidebar">')
cat('<h3>📑 Filter by Feed</h3>')
cat('<ul class="feed-list">')

# "All Feeds" option
cat(sprintf('<li class="feed-item active" data-feed="all" onclick="filterFeed(\'all\')">
  All Feeds <span class="feed-count">%d</span>
</li>', total_articles))

# Individual feed options
for (i in 1:nrow(feed_counts)) {
  feed <- feed_counts[i, ]
  # Create a safe ID from the feed name
  feed_id <- gsub("[^a-zA-Z0-9]", "-", feed$source)

  cat(sprintf('<li class="feed-item" data-feed="%s" onclick="filterFeed(\'%s\')">
  %s <span class="feed-count">%d</span>
</li>',
    feed_id,
    feed_id,
    htmltools::htmlEscape(feed$source),
    feed$count
  ))
}

cat('</ul>')
cat('</aside>')

# === MAIN CONTENT: Article List ===
cat('<main class="main-content">')

if (nrow(articles) == 0) {
  cat('<div class="empty-state">')
  cat('<p>No articles available. Check your RSS feeds configuration.</p>')
  cat('</div>')
} else {
  cat('<div id="article-list">')

  # Render each article with data attribute for filtering
  for (i in 1:nrow(articles)) {
    article <- articles[i, ]
    feed_id <- gsub("[^a-zA-Z0-9]", "-", article$source)

    # Show first 20 articles, hide the rest initially
    display_class <- if (i <= 20) "article-card" else "article-card hidden"

    cat(sprintf('
<article class="%s" data-feed="%s" data-index="%d">
  <div class="article-header">
    <span class="article-source">%s</span>
    <span class="article-time">%s</span>
  </div>
  <h2 class="article-title">
    <a href="%s" target="_blank" rel="noopener">%s</a>
  </h2>
  <p class="article-excerpt">%s</p>
</article>
',
      display_class,
      feed_id,
      i,
      htmltools::htmlEscape(article$source),
      htmltools::htmlEscape(article$time_ago),
      htmltools::htmlEscape(article$link),
      htmltools::htmlEscape(article$title),
      htmltools::htmlEscape(article$excerpt)
    ))
  }

  cat('</div>')

  # Load More button (only show if > 20 articles)
  if (nrow(articles) > 20) {
    cat(sprintf('<button class="load-more-btn" onclick="loadMore()" id="load-more-btn">
  Load More Articles (%d remaining)
</button>', nrow(articles) - 20))
  }
}

cat('</main>')
cat('</div>')  # Close page-container
```

<script>
// Track currently visible count
let currentlyVisible = 20;
let currentFilter = 'all';

// Filter articles by feed
function filterFeed(feedId) {
  currentFilter = feedId;
  currentlyVisible = 20;

  // Update active state in sidebar
  document.querySelectorAll('.feed-item').forEach(item => {
    if (item.dataset.feed === feedId) {
      item.classList.add('active');
    } else {
      item.classList.remove('active');
    }
  });

  // Filter articles
  const articles = document.querySelectorAll('.article-card');
  let visibleCount = 0;

  articles.forEach((article, index) => {
    const articleFeed = article.dataset.feed;
    const shouldShow = (feedId === 'all' || articleFeed === feedId);

    if (shouldShow) {
      visibleCount++;
      if (visibleCount <= 20) {
        article.classList.remove('hidden');
      } else {
        article.classList.add('hidden');
      }
    } else {
      article.classList.add('hidden');
    }
  });

  // Update load more button
  updateLoadMoreButton();
}

// Load more articles
function loadMore() {
  const articles = document.querySelectorAll('.article-card');
  let visibleCount = 0;
  let shownCount = 0;

  articles.forEach(article => {
    const articleFeed = article.dataset.feed;
    const shouldShow = (currentFilter === 'all' || articleFeed === currentFilter);

    if (shouldShow) {
      visibleCount++;
      if (!article.classList.contains('hidden')) {
        shownCount++;
      } else if (shownCount < currentlyVisible + 20 && visibleCount > currentlyVisible) {
        article.classList.remove('hidden');
        shownCount++;
      }
    }
  });

  currentlyVisible = shownCount;
  updateLoadMoreButton();
}

// Update load more button state
function updateLoadMoreButton() {
  const btn = document.getElementById('load-more-btn');
  if (!btn) return;

  const articles = document.querySelectorAll('.article-card');
  let totalMatching = 0;
  let currentlyShown = 0;

  articles.forEach(article => {
    const articleFeed = article.dataset.feed;
    const shouldShow = (currentFilter === 'all' || articleFeed === currentFilter);

    if (shouldShow) {
      totalMatching++;
      if (!article.classList.contains('hidden')) {
        currentlyShown++;
      }
    }
  });

  const remaining = totalMatching - currentlyShown;

  if (remaining > 0) {
    btn.style.display = 'block';
    btn.textContent = `Load More Articles (${remaining} remaining)`;
  } else {
    btn.style.display = 'none';
  }
}
</script>

::: {.footer-note}
This is a static site generated with [Quarto](https://quarto.org) and R.
All RSS feeds are fetched server-side with minimal client-side filtering.
:::
